Keep your Laziness in Check

### 2018-03-10 paper/main.tex
More writing on the rot example

On the other hand, if the output demand is larger than the first list,
then \textit{all} of the spine of second argument has to be evaluated.
%
\rotex{[1,2,3]}{[6,5,4]}{[1,2,3,4,5,6]}
      {\X1 : \X2 : \X3 : \X4 : \_}{ [ \X1 , \X2 , \X3 ] } { [ \_ , \_ , \X4 ] }
%
The predicted demand on the first list will be the top part of the
demand of length equal to \lk{length fs}. The predicted demand on the
second list will be the reverse of the remaining demand, padded with
thunks if necessary.
\leo{One more tricky case, when the demand on the output forces
the null constructor of the bs list. How do we talk about that?}

Now we can give the actual StrictCheck specification
of \lk{rot\_simple}:

\leo{Debug the stupid spec and add it and describe it}

>>>>

On the other hand, if the output demand is larger than the first list,
then \textit{all} of the spine of second argument has to be evaluated.
%
\rotex{[1,2,3]}{[6,5,4]}{[1,2,3,4,5,6]}
      {\X1 : \X2 : \X3 : \X4 : \_}{ [ \X1 , \X2 , \X3 ] } { [ \_ , \_ , \X4 ] }
%
The predicted demand on the first list will be the top part of the
demand of length equal to \lk{length fs}. The predicted demand on the
second list will be the reverse of the remaining demand, padded with
thunks if necessary.

The two cases above give rise to the following StrictCheck specification:
%
\begin{inlinecode}
rot_simple_spec :: (Show a, Shaped a) => Spec '[[a], [a]] [a]
rot_simple_spec =
  Spec $ \predict d fs bs ->
    let demandOnFs
          | length (cap d) > length fs =
              take (length fs) d
          | otherwise = d
        demandOnBs
          | length (cap d) > length fs =
              reverse $ take (length bs)
                      $ (drop (length fs) (cap d)) ++ repeat thunk
          | otherwise = thunk
    in predict demandOnFs demandOnBs
\end{inlinecode}
%
Just like the \lk{take\_spec} of the introduction, this specification
is the constructor \lk{Spec} applied to a function that takes a
function \lk{predict}, the output demand \lk{d}, as well as the actual
input lists \lk{fs} and \lk{bs} and \lk{predict}s the demand
on \lk{fs} and \lk{bs}. In particular, if we don't demand more from
the output of \lk{rot\_simple} than the length of \lk{fs} then the
demand on \lk{fs} is just \lk{d} itself, while \lk{bs} is left
completely unevaluated. On the other hand, if we do, only the first
half of the demand is actually relevant to \lk{fs}, while the rest
constitutes the demand on \lk{bs} after being appropriately padded
with thunks if necessary and reversed.

Let's test this specification!
%
\leo{Screengrab bug? How did you do the other one?}
%
StrictCheck quickly reveals a bug: when the output demand is
spinestrict and the back list \lk{bs} is empty, then the second list
will also be forced to ensure it is of the correct shape
(\lk{[]}). \leo{TODO: corrected spec. Thinking side-by-side figure
with the next one?}
